---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Philip Picard"
date: "8/29/2019"
output: html_document
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

1846 rows and 3 columns. The variables are: dataset, x, and y.

### Exercise 2

Get the data we need and filter out anything that is not part of the "dino" dataset. We will then
tell R how to display it (with a plot).

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Finally calculate the the relation between x and y.

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Filter out any data not part of the "star" set and place that data in star_data. Then we will tell 
R how to display the data.

```{r plot-star, fig.height=3, fig.width=6}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Calculate the r between x and y from the star_data.

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

### Exercise 4

Filter out any data not part of the "circle" set and place that data in circle_data. Then we will tell 
R how to display the data.

```{r plot-circle, fig.height=3, fig.width=6}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Calculate the r between x and y from the circle_data.

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.)