---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Philip Picard"
date: "8/29/2019"
output: 
  html_document: 
    fig_height: 8
    fig_width: 10
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

1846 rows and 3 columns. The variables are: dataset, x, and y.

### Exercise 2

Get the data we need and filter out anything that is not part of the "dino" dataset. We will then
tell R how to display it (with a plot).

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Finally calculate the the relation between x and y.

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Filter out any data not part of the "star" set and place that data in star_data. Then we will tell 
R how to display the data.

```{r plot-star, fig.height=3, fig.width=6}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Calculate the r between x and y from the star_data.

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

### Exercise 4

Filter out any data not part of the "circle" set and place that data in circle_data. Then we will tell 
R how to display the data.

```{r plot-circle, fig.height=3, fig.width=6}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Calculate the r between x and y from the circle_data.

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```

### Exercise 5

Plot all the datasets instead of just one.

```{r plot-all}
ggplot(data = datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
```

Group all the datasets and then get the r between x and y for each dataset.

```{r group-all}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```